\Russell's Metatheoretic Study - Notes

### 2006-05-31 papers/slides-ICFP'06/notes.tex
Added notes for ICFP

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{xspace} % To get the right spacings in front of : and so on
\usepackage[english]{babel}
\usepackage{abbrevs}
\usepackage{subfigure}
\usepackage{ifthen}
\usepackage{coqdoc}
\usepackage{bussproofs}
\usepackage{pgf,pgfarrows,pgfnodes}
\usepackage{concmath}
\usepackage{url}
\usepackage{fullpage}

\title{\Russell's Metatheoretic Study - Abstract}
\date{\today}
\author{Matthieu Sozeau \\
  LRI - Paris Sud - XI University \\
  sozeau@lri.fr}
\begin{document}
\maketitle

We are working on the formalization of \Russell{}'s type theory in the
\Coq{} proof assistant \cite{sozeau:coq/Russell/meta}.  The type system
of \Russell{} is based on the Calculus of Constructions with
$\Sigma$-types (dependent sums), extended by an equivalence on types
which subsumes $\beta$-conversion. The extension permits to identify
types and subsets based on them in a manner similar to the
\emph{Predicate Subtyping} feature of \PVS{}.

@@

\item Correction of the traduction: the target system include
  metavariables, introducing a second, \emph{unusual} kind of variable binding.
\end{itemize}

We will present these difficulties and our recipes for solving them in
the \Coq environment. Additionaly, we will identify more general problems for
proving in \Coq and suggest possible solutions.

{\bf Disclaimer}: this is a work in
progress ; to this day we have proved elimination of transivity and
subject reduction should follow soon.

>>>>

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{xspace} % To get the right spacings in front of : and so on
\usepackage[english]{babel}
\usepackage{abbrevs}
\usepackage{subfigure}
\usepackage{ifthen}
\usepackage{coqdoc}
\usepackage{bussproofs}
\usepackage{pgf,pgfarrows,pgfnodes}
\usepackage{amsmath}
\usepackage{concmath}
\usepackage{url}
\usepackage{fullpage}

\def\tactic#1{\texttt{#1}}

\title{\Russell's Metatheoretic Study - Notes}
\date{\today}
\author{Matthieu Sozeau \\
  LRI - Paris Sud - XI University \\
  sozeau@lri.fr}
\begin{document}
\maketitle
\begin{abstract}
We are working on the formalization of \Russell{}'s type theory in the
\Coq{} proof assistant \cite{sozeau:coq/Russell/meta}.  The type system
of \Russell{} is based on the Calculus of Constructions with
$\Sigma$-types (dependent sums), extended by an equivalence on types
which subsumes $\beta$-conversion. The extension permits to identify
types and subsets based on them in a manner similar to the
\emph{Predicate Subtyping} feature of \PVS{}.

@@

\item Correction of the traduction: the target system include
  metavariables, introducing a second, \emph{unusual} kind of variable binding.
\end{itemize}
\end{abstract}

- Works only with $``>=$ coq-v8.2.

\begin{itemize}
\item Work on a dependency analyser for terms.
\item Problem of mutual induction, conjunction of goals, generating the
  principle and applying it.
\item Problem of induction on partially instanciated goals, see McBride.
\item Induction on depths:
  \begin{itemize}
  \item Adding a parameter on judgements.
  \item Adding a parameter and going in \Set.
  \end{itemize}
\item Useful tactics: \tactic{subst}, \tactic{eauto}, \tactic{generalize dependent}.
\item Reusability of proofs (multiple systems).
\end{itemize}
